BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-04-25 tex/main.tex
Minor typos and reformulations
Invert legend order on the grnuplot figure
Fix two typos
Formatting revisions
Hardcode the bibliography to adjust margins
Update license

% Toggle comment this line, the url and the hyperref package
% to generate a PDF/X-1a compliant output.
% \usepackage[x-1a]{pdfx}

\parindent 0pt
\usepackage[ruled, vlined]{algorithm2e}
\parindent 10pt
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[autostyle=false, style=english]{csquotes}
\usepackage[usenames,dvipsnames]{color}
\usepackage[justification=centering]{caption}
\usepackage[nodayofweek]{datetime}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{balance}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{gnuplottex}
\usepackage{quoting}
\usepackage{sepfootnotes}
\usepackage{setspace}
\usepackage[hyphens]{url}
\usepackage[pdfpagelabels=false]{hyperref}
\usepackage{hypcap}

\MakeOuterQuote{"}
\setenumerate{noitemsep, topsep=10pt, parsep=6pt,partopsep=0pt}
\setitemize{noitemsep,topsep=10pt, parsep=6pt, partopsep=0pt}
\def\algorithmautorefname{Algorithm}
\graphicspath{{img/}}

\newdateformat{lv}{\THEDAY{ }\shortmonthname[\THEMONTH] \THEYEAR}
\newcommand{\lastvisited}{Last visited \lv\today}
\newcommand\TODO[1]{\emph{\color{Red} TODO: #1}}
\newcommand\noop[1]{\emph{\emph{#1}}}
\newcommand\edit[1]{\emph{\color{Green}#1}}
\newcommand\code[1]{\texttt{#1}}
\newcommand\coderef[1]{\texttt{\ref{#1}}}
\newcommand\stringliteral[1]{\texttt{\char`\"#1\char`\"}}
\newcommand\len[1]{|#1|}
\newcommand\set[1]{\{#1\}}
\newcommand\surl[1]{\urlstyle{ff}\url{#1}}
\newcommand\Oof[1]{$\mathcal{O}(#1)$}

@@

  \conferenceinfo{WIMS'14,}{June 2-4, 2014 Thessaloniki, Greece}
  \CopyrightYear{2014}
  \crdata{978-1-4503-2538-7/14/06}

@@

@@

  \bibliographystyle{abbrv}
  \bibliography{short}

>>>>

\parindent 0pt
\usepackage[ruled, vlined]{algorithm2e}
\parindent 10pt
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[autostyle=false, style=english]{csquotes}
\usepackage[usenames,dvipsnames]{color}
\usepackage[nodayofweek]{datetime}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage[tableposition=top, font=bf]{caption}
\usepackage{balance}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{gnuplottex}
\usepackage{ifthen}
\usepackage{quoting}
\usepackage{sepfootnotes}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage[hyphens]{url}
\usepackage[pdfpagelabels=false,draft=true]{hyperref}
\usepackage{hypcap}

\MakeOuterQuote{"}
\def\algorithmautorefname{Algorithm}

\newdateformat{lv}{\THEDAY{ }\monthname[\THEMONTH] \THEYEAR}
\newcommand{\lastvisited}{Last visited \lv\today}
\newcommand\TODO[1]{\emph{\color{Red} TODO: #1}}
\newcommand\noop[1]{\emph{\emph{#1}}}
\newcommand\edit[1]{\emph{\color{Green}#1}}
\newcommand\code[1]{\texttt{#1}}
\newcommand\coderef[1]{\texttt{\ref{#1}}}
\newcommand\stringliteral[1]{\texttt{\char`\"#1\char`\"}}
\newcommand\len[1]{|#1|}
\newcommand\set[1]{\{#1\}}
\newcommand\surl[1]{\urlstyle{ff}\url{#1}}
\newcommand\Oof[1]{$\mathcal{O}(#1)$}
\newboolean{fref}

@@

  \permission{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than the author(s) must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from Permissions@acm.org.}

  \conferenceinfo{WIMS'14,}{June 02-04, 2014 Thessaloniki, Greece}
  \crdata{978-1-4503-2538-7/14/06}
  \newcommand{\doi}{http://dx.doi.org/10.1145/2611040.2611067}

  \global\copyrightetc{Copyright is held by the owner/authors. Publication rights licensed to ACM. ACM \the\acmcopyr\$15.00.\\\doi}

@@

  \vspace{3pt}

@@

  \def\changemargin{\list{}{\leftmargin3pt}\item[]}
  \let\endchangemargin=\endlist
  \let\oldbibitem\bibitem

  \setboolean{fref}{true}
  \renewcommand\bibitem[1]{
    \ifthenelse{\boolean{fref}}{
      \setboolean{fref}{false}
      \vspace{4pt}
      \oldbibitem{#1}
      \begin{changemargin}
    }{
      \end{changemargin}
      \oldbibitem{#1}
      \begin{changemargin}
    }
  }

  \bibliographystyle{abbrv}
  \input{hardcoded.bbl}
  % \bibliography{short}
